ext_risk_copula

### 2019-01-26 Paper.Rmd

To keep $Var(P_{i}(t+1))$ equal to unity, we set noise coefficient $\alpha$ in terms of AR coefficient $\beta$ as $\alpha = \sqrt(1-\beta^2)$. We showed with Eq. \ref{eq.AR1} in the next section that non-parametric analysis indicated similar tail dependence in population copula as that of noise copula. 
<!--Asymmetric sensitivity and copula structure in populations-->
\textbf{(ii)} Secondly, we intended to see if any specific (lower or upper) tail dependence emerges from a copula of two meta-populations, due to some global environmental factors (like temperature or snowfall) which behaved differently beyond a certain expectation threshold (as shown in Eq. \ref{eq.AS_g}). To test the assymetric sensitivity, we constructed a two habitat patch model for population $P_{i} (i=1,2)$ as follows;

>>>>

To keep $Var(P_{i}(t+1))$ equal to unity, we set noise coefficient $\alpha$ in terms of AR coefficient $\beta$ as $\alpha = \sqrt(1-\beta^2)$. We showed with Eq. \ref{eq.AR1} in the next section that both model selection method and non-parametric analysis indicated similar tail dependence in population copula as that of noise copula. <!--Asymmetric sensitivity and copula structure in populations-->
\textbf{(ii)}

The second mechanism, which was also summarized in the introduction,
relates to Liebig's law of the minimum, or, more generally, to the potential for 
environmental variables to influence ecological variables through nonlinear relationships.

Secondly, we intended to see if any specific (lower or upper) tail dependence emerges from a copula of two meta-populations, due to some global environmental factors (like temperature or snowfall) which behaved differently beyond a certain expectation threshold (as shown in Eq. \ref{eq.AS_g}). To test the assymetric sensitivity, we constructed a two habitat patch model for population $P_{i} (i=1,2)$ as follows;

### 2019-01-26 ext_risk_copula.Rmd

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf",heigh=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="hassell",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf",heigh=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="hassell",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

>>>>

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf",heigh=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="hassell",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf",heigh=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="hassell",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```
